\Large{Research Seminar Software Science} \\ \huge{Monads}

### 2018-04-16 paper.tex
added subsection on laziness

\subsection{Lazy}
\end{document}

>>>>

\subsection{Lazy Evaluation}

Haskell is a functional language with non-strict semantics. What does this mean? An expression is evaluated from the outside in. For instance, the evaluation of \textit{$(a + (b * c))$} will firstly reduce the \textit{$+$} operator and then the inner bracket \textit{$(a * b)$}. \\
Lazy evaluation is just an implementation approach for a non-strict language. An appropriate definition for laziness can be represented by the term \textit{call-by-need}. Consequently, the evaluation of an expression is delayed until its result is actually needed from another computation. Therefore, the parameters of a function are evaluated only when they are needed and not a moment before. 
\end{document}
